An Invariant Framework for Conducting Reproducible Computational Science

### 2015-01-14 measure.tex
Changes to RW

 % Docker images
\vspace{5pt}
\noindent{\bf Linux Containers and Docker Images}

Linux Containers provide multiple isolated execution instances on top of the same kernel through OS-level virtualization. Thus they can be used to persist the captured packages into images. Using such containers, Docker now allows to preserve the image in a more user-friendly way. In particular, apart from performing Linux container (LXC) based operating system (OS) level virtualization, docker tools provides portable deployment of containers across platforms, documentation of packages in a scriptable format, and versioning of container images. The image can be preserved along with dockerfiles, which are plain text files with a literate programming environment: the computational part is similar to shell scripts and can help provision similar to other provisioning tools (e.g. Chef, Puppet) or Continuous Integration (CI) platforms (e.g. Travis CI), and the text part is for human consumption and more suited for use with a version management system such as subversion or git, which can track any changes made to the Dockerfile. Thus dockerfiles can be used to preserve the namelist of Parrot packages and provenance description in PTU. 
Docker is integrated with a continuous build environment which will check and validate the version of the software being used, and use a more recent version to build application software.

@@

\section{Measuring Dependencies}

\begin{figure*}
\centering
\includegraphics[width=.8\textwidth]{workflow-parrot.eps}
\caption{Workflow of The Fine-Grained Dependency Management Toolkit Based on Parrot}
\label{fig:workflow-parrot}
\end{figure*}

>>>>

 % Docker images
\vspace{5pt}
\noindent{\bf Linux Containers and Docker Images:} Linux Containers provide multiple isolated execution instances on top of the same kernel through OS-level virtualization. Thus they can be used to persist the captured packages into images. Using such containers, Docker now allows to preserve the image in a more user-friendly way. In particular, apart from performing Linux container (LXC) based operating system (OS) level virtualization, docker tools provides portable deployment of containers across platforms, documentation of packages in a scriptable format, and versioning of container images. The image can be preserved along with dockerfiles, which are plain text files with a literate programming environment: the computational part is similar to shell scripts and can help provision similar to other provisioning tools (e.g. Chef, Puppet) or Continuous Integration (CI) platforms (e.g. Travis CI), and the text part is for human consumption and more suited for use with a version management system such as subversion or git, which can track any changes made to the Dockerfile. Thus dockerfiles can be used to preserve the namelist of Parrot packages and provenance description in PTU. 
Docker is integrated with a continuous build environment which will check and validate the version of the software being used, and use a more recent version to build application software.

@@

\begin{figure*}
\centering
\includegraphics[width=.8\textwidth]{preservation_framework.eps}
\caption{Preservation Framework}
\label{fig: preservation_framework}
\end{figure*}

%\section{Measuring Dependencies}

### 2015-01-14 paper.tex
Changes to RW

\begin{abstract}
\it Computational reproducibility depends on being able to isolate necessary and sufficient computational artifacts and preserve them for later re-execution.
Both isolation and preservation of artifacts can be challenging due to the complexity
of existing software and systems and the resulting implicit dependencies, resource distribution, and shifting compatibility of systems as time progresses---all conspiring
to break the reproducibility of an application. Sandboxing is a technique
that has been used extensively in OS environments for isolation of computational artifacts.
Several tools were proposed recently that employ sandboxing as a mechanism to ensure reproducibility.
However, none of these tools preserve the sandboxed application for re-distribution
to a larger scientific community---aspects that are equally crucial for ensuring reproducibility as sandboxing itself.
In this paper, we describe a combined sandboxing and preservation framework, which is efficient, invariant and
practical for large-scale reproducibility. We present case studies of complex high energy
physics applications and show how the framework can be useful for sandboxing, preserving and distributing applicatios.
We report on the completeness, performance,
and efficiency of the framework, and suggest possible standardization approaches.
\end{abstract}

@@

\input {intro}
\input {tauroast}
\input {observation}
\input {evolution}
%\input {measure}
\input {evaluation}
\input {problems}
\input {related_work}
%\input {postscript}

>>>>

\begin{abstract}
\it Computational reproducibility depends on being able to isolate necessary and sufficient computational artifacts and preserve them for later re-execution.
Both isolation and preservation of artifacts can be challenging due to the complexity
of existing software and systems and the resulting implicit dependencies, resource distribution, and shifting compatibility of systems as time progresses---all conspiring
to break the reproducibility of an application. Sandboxing is a technique
that has been used extensively in OS environments for isolation of computational artifacts.
Several tools were proposed recently that employ sandboxing as a mechanism to ensure reproducibility.
However, none of these tools preserve the sandboxed application for re-distribution
to a larger scientific community---aspects that are equally crucial for ensuring reproducibility as sandboxing itself.
In this paper, we describe a combined sandboxing and preservation framework, which is efficient, invariant and
practical for large-scale reproducibility. We present case studies of complex high energy
physics applications and show how the framework can be useful for sandboxing, preserving and distributing applications.
We report on the completeness, performance,
and efficiency of the framework, and suggest possible standardization approaches.
\end{abstract}

@@

\input {intro}
\input {tauroast}
\input {observation}
\input {evolution}
\input {measure}
\input {evaluation}
\input {problems}
\input {related_work}
%\input {postscript}
